Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-07-26 SupportingInformation.Rmd
modified

```{r call_cop_pedag_fig,echo=F,results="hide",cache=T, cache.extra=list(seed,mtime("copula_pedag_fig.R"))}
set.seed(seed)
source("./copula_pedag_fig.R")

#cat(paste("start-time: ",Sys.time(),"\n"))
df<-cop_est_2par(fam=7,p1range = c(0.01:7),p2range = c(1:7),incr = 0.005)
saveRDS(df,"./Results/df_fam7_incr_0.005.RDS")
#cat(paste("stop-time: ",Sys.time(),"\n"))

df_fam7<-readRDS("./Results/df_fam7_incr_0.005.RDS")
#range(df_fam7$LTmUT)

>>>>

```{r call_cop_pedag_fig,echo=F,cache=T, cache.extra=list(seed,mtime("copula_pedag_fig.R"))}
set.seed(seed)
source("./copula_pedag_fig.R")

#cat(paste("start-time: ",Sys.time(),"\n"))
df<-cop_est_2par(fam=7,p1range = c(0.01:7),p2range = c(1:7),incr = 0.005)
saveRDS(df,"./Results/df_fam7_incr_0.005.RDS")
#cat(paste("stop-time: ",Sys.time(),"\n"))
```

```{r cop_pedag_fig,echo=F,results="hide"}
df_fam7<-readRDS("./Results/df_fam7_incr_0.005.RDS")
#range(df_fam7$LTmUT)
